Environment affects specialisation of plants and pollinators

### 2019-11-30 paper/manuscript.Rmd
Improve wording sensitivity analysis in Methods

We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental suitability values in our communities. 
For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.

>>>>

We used a sensitivity analysis to determine the minimum number of occurrences that are necessary to have robust environmental stress estimations. 
For that we used the species with most occurrences available, *`r sensitivity_species_name$canonicalName`*, and calculated the mean absolute error of the bioclimatic suitability values obtained with `r numbers2words(config$n_subsamples)` subsamples from the `r format(n_occ_sensitivity_species, big.mark  =",")`  occurrences available from GBIF.
